---
output: rmarkdown::github_document
---

`scimple` : Tidy Simultaneous Confidence Interval for Multinomial Proportion

This is a tidy version of the `CoinMinD` R package with some extra bits tossed in for good measure.

The following functions are implemented:

- `scimple_ci`: Calculate multiple simultaneous confidence intervals using selected methods (excluding Bayesian methods)
- `scimp_bmde`:	Bayesian Multinomial Dirichlet Model (Equal Prior)
- `scimp_bmdu`:	Bayesian Multinomial Dirichlet Model (Unequal Prior)
- `scimp_fs`:	Fitzpatrick and Scott Confidence Interval
- `scimp_goodman`:	Goodman Confidence Interval
- `scimp_qh`:	Quesenberry & Hurst Confidence Interval
- `scimp_sg`:	Sison & Glaz Confidence Interval
- `scimp_wald`:	Wald Confidence Interval
- `scimp_waldcc`:	Wald Confidence Interval (with continuity correction)
- `scimp_wilson`:	Wilson Confidence Interval

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/scimple")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

### Usage

```{r message=FALSE, warning=FALSE, error=FALSE, fig.width=10, fig.height=5.5, fig.retina=2}
library(scimple)
library(hrbrthemes)
library(tidyverse)

# current verison
packageVersion("scimple")

y <- c(44,55,43,32,67,78)
z <- 0.05

cis <- scimple_ci(y, z)

print(cis)

ggplot(cis) +
  geom_segment(aes(x=lower_limit, xend=upper_limit, y=method, yend=method, color=method)) +
  scale_color_ipsum(name=NULL) +
  facet_wrap(~inpmat, scales="free_x") +
  labs(x=NULL, y=NULL, 
       title="Multipe simultaneous confidence intervals",
       subtitle="Note free X scale") +
  theme_ipsum_rc(grid="X") +
  theme(legend.position="bottom")
```

### Test Results

```{r message=FALSE, warning=FALSE, error=FALSE}
library(scimple)
library(testthat)

date()

test_dir("tests/")
```
